More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
proof and lemma

@@

\TODO{From Definition \ref{def:buildweakOT} we can prove following lemma that enables us to conclude FH-weak bisimulation coincides with  FH-bisimulation ... what does coincide mean here?}

\begin{lemma} \TODO{!!! formalisation of the lemma is cumbersome}
$s (\OTarrow{\tau})\!\!* (\OTarrow{\alpha})(\OTarrow{\tau})\!\!* s'$ iff $s \OTWeakarrow {\alpha} s'$
\end{lemma}

\begin{proof} ($\Rightarrow$)

@@

----------------------------------------------

@@

\subsection{Weak bisimulation is an equivalence}
\TODO{moved from body}

>>>>

We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})\!* (\OTarrow{\alpha})(\OTarrow{\tau})* $.

@@

@@

@@

\subsection{Weak bisimulation is an equivalence}

\begin{lemma} Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ be open automata and $<J,\mathcal{S}_1, s_0,
    \WT_1>$ be the
weak open automata derived from $A_1$.

\begin{itemize}
 \item  For any weak open transition $\symb{WOT} \in \WT$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}

there exists  open transitions $\symb{OT} \in \mathcal{T}$:

\begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 or $s=s'$ and $\alpha = \tau$
\end{itemize}

\begin{proof} 
We can rewrite $s \OTWeakarrow {} s'$ as follows $s \OTarrow {} s_1 \OTarrow {} \ldots \OTarrow {} s_n  \OTarrow {} s'$, we proceed by induction on the length of the inference of  ${s \OTWeakarrow {\alpha} s'}$ (introduced in Definition \ref{def:buildweakOT}). First, if  $\overline{\gamma}=\emptyset$ then using rule (1) we can directly conclude  $s=s'$ and $\alpha =\tau$. Otherwise, using  rule (2)  we have  s $\OTarrow {\alpha} s'$ and forall $j$, $\gamma_j=\vis{\beta_j}$. Second, using rule (3)  we have ${s \OTWeakarrow {\alpha} s'}$ implies ${s \OTWeakarrow {\tau} s_1} \OTWeakarrow {\alpha} s_2  \OTWeakarrow {\tau} s'$ and forall $j$, $\gamma_j = \gamma_{1j}\,\dotcup\,\gamma_{2j}\,\dotcup\,\gamma_{3j}$, and by induction hypothesis this means that there exist $s, s'$  such that $ s \OTarrow {\alpha} s'$ and $j$, $\gamma_{2j}=\vis{\beta_j}$.
\end{proof}   
\end{lemma}

\TODO{I am not sure that we have the same states between open auto and weak auto}

Using this lemma, it is straightforward to see that....  
\begin{lemma}
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
If $A_1$ and $A_2$ are weak FH-bisimilar then 
\begin{itemize}
 \item  For any weak open transition $\symb{WOT} \in \WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}

there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x. \gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

\end{itemize}
\end{lemma}

\TODO{moved from body}
